The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-08-13 albatros_paper.tex
HCC added author list

\markboth{Author's Name}{ALBATROS instrument}

@@

\author{First Author$^{2}$, Second Author$^{3}$, Third Author$^{3}$ and Fourth Author$^{4}$}

\address{
$^{2}$Department, University Name, City, State ZIP/Zone, Country, fauthor@university.com\\
$^{3}$Group, Company, Address, City, State ZIP/Zone, Country\\
$^{4}$Group, Company, Address, City, State ZIP/Zone, Country, fauthor@company.com
}

@@

\corres{$^{2}$Corresponding author.}

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.6\linewidth]{Figures/marion_domec_hobart.png}
    \caption{Minimum plasma frequency predicted by the International
      Reference Ionosphere model during the last solar minimum.  At
      some locations on Earth, the plasma frequency may drop as low as
      $\sim1.5$~MHz.}
    \label{Fig:iri}
  \end{center}
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/corr_efficiency/corr_efficiency.png}
    \caption{Correlator efficiency $\epsilon$ for a 1-bit correlator
      as a function of signal-to-noise ratio (SNR).  The efficiency is
      roughly 0.64 at low SNR and drops monotonically as the SNR
      increases.  The decrease in $\epsilon$ is relatively gentle,
      changing by only a factor of 2 for SNR $\sim2$.}
    \label{fig:1bit_efficiency}
    \end{center}
\end{figure}

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
    \caption{Phases from the cross-correlation between two co-aligned
      polarizations in the two-element \albatros\ pathfinder.  About
      372 hours of data are shown here, binned in local sidereal
      time.}
    \label{Fig:albatros2_phase}
  \end{center}
\end{figure}

>>>>

\markboth{H.~C.~Chiang et al.}{ALBATROS instrument}

@@

\author{H.~C.~Chiang$^{1,2,\dagger}$, T.~Dyson$^{1}$, E.~Egan$^{1}$,
  S.~Eyono$^{2}$, N.~Ghazi$^{2}$, J.~Hickish$^{3}$,
  J.~M.~J\'auregui--Garcia$^{4}$, V.~Manukha$^{5}$, T.~Moso$^{2}$,
  J.~Peterson$^{4}$, L.~Philip$^{6}$, J.~L.~Sievers$^{1,6}$,
  S.~Tartakovsky$^{1}$}

\address{
$^{1}$Department of Physics, McGill University, Montr\'eal, Quebec H3A 2T8, Canada\\
$^{2}$School of Mathematics, Statistics, and Computer Science,
  University of KwaZulu--Natal, Durban 4000, South Africa\\
$^{3}$Department of Astronomy, University of California, Berkeley,
  California 94720, USA\\
$^{4}$Department of Physics, Carnegie Mellon University,
  Pittsburgh, Pennsylvania 15213, USA\\
$^{5}$South African National Space Agency, Hermanus 7200, South Africa\\
$^{6}$School of Chemistry and Physics,
  University of KwaZulu--Natal, Durban 4000, South Africa
}

@@

\corres{$^{\dagger}$Corresponding author: hsin.chiang@mcgill.ca}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.63\linewidth]{Figures/marion_domec_hobart.png}
    \caption{Minimum plasma frequency predicted by the International
      Reference Ionosphere model during the last solar minimum.  At
      some locations on Earth, the plasma frequency may drop as low as
      $\sim1.5$~MHz.}
    \label{Fig:iri}
  \end{center}
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.75\linewidth]{Figures/corr_efficiency/corr_efficiency.png}
    \caption{Correlator efficiency $\epsilon$ for a 1-bit correlator
      as a function of signal-to-noise ratio (SNR).  The efficiency is
      roughly 0.64 at low SNR and drops monotonically as the SNR
      increases.  The decrease in $\epsilon$ is relatively gentle,
      changing by only a factor of 2 for SNR $\sim2$.}
    \label{fig:1bit_efficiency}
    \end{center}
\end{figure}

@@

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{Figures/albatros2_lst_phase.jpg}
    \caption{Phases from the cross-correlation between two co-aligned
      polarizations in the two-element \albatros\ pathfinder.  About
      372 hours of data are shown here, binned in local sidereal
      time.}
    \label{Fig:albatros2_phase}
  \end{center}
\end{figure}
